\chapter{Introduction}

\vspace{10mm}
\section{Background to the study}
\vspace{5mm}
With advancements in technology, the demand for a robotic solution when problem solving is increasing fast and is already in high demand. Unfortunately the current hardware available in the market for accurate motor control is expensive, resulting in the only consumers who have access to it, being the large companies and other organisations with big budgets. This limits those individuals who want to design and prototype robotic applications at home or at university for research projects. 

These motor controller boards allow for more advanced control of the motor, not just direction control, they also allow for velocity, current and torque control with the aid of additional sensors. This helps give better performance and a higher accuracy of motor control. , allowing for more advanced robotic application.

There is a high demand for robotic software and hardware but until recent years it has been unaffordable for the general public. The aim of this study is to design and create an affordable servomotor controller board that will have all the functionality alike that of the more expensive controllers, but be much cheaper.   

\newpage
\section{Objectives of this study}
This project illustrates the design and production of a servomotor controller board. On-board sensors and microcontroller will be used to monitor temperature and current drawn as well as allow for motor control. The controller will be able designed to be cable of connecting to a wide range of servomotors as well as allowing multiple boards to be daisy chained together and be capable of serial communication. Advanced servomotor controllers are expensive. The designed board needs to have the abilities of the more expensive controllers, but be much cheaper. 

\vspace{5mm}
\section{Scope and Limitations}
The design of the controller board was performed from an academic view-point. The main goal being to create a proof of concept, showing that it is possible for cheaper servomotor controllers to be designed with the same functionality of more expensive controller boards.

\vspace{5mm}
\section{Plan of development}
This report is organised in the following order. First the objectives of the study and the problem to be solved are outlined in the Introduction. Second, a review of available literature on the topic at hand. The required system is then designed and components are chosen. The components are tested and the method and results are discussed. The PCB is the designed and the component placement and testing is discussed. The methods for the implementation of the code is discussed and then finally comclusion are drawn and recommendations were made. 



